### 2014-12-02 writing/F'14 paper/intro.tex
Paper TODO tweaks

% TODO: Do we need both of these Icard/Moss citations? -- I'd prefer
% to keep them ---CP.

% Since no existing model architecture can be adopted without modification
% to handle entailment classification, we describe a novel method for this task
% in the spirit of prior work on recursive neural networks (\ref{methods}).
In our first set of experiments, we use this pre-specified logical
grammar to generate controlled data sets encoding the semantic
relationships between pairs of expressions and evaluate whether each
of two classes of neural model---plain RNNs and recursive neural
tensor networks (RNTNs; \cite{socher2013acl1})---can learn those
relationships correctly. In our first experiment
(Section~\ref{sec:join}), we evaluate the ability of these models to
learn the core relational algebra of natural logic from data. Our
second experiment (Section~\ref{sec:recursion}) extends this
evaluation to relations between complex recursive structures like
$(a \plor b)$ and $\plneg (\plneg a \pland \plneg b)$, and our third
experiment (Section~\ref{sec:quantifiers}) involves relations between
quantified statements like \ii{every reptile walks} and \ii{no turtle
  moves}. \tbchecked{We find that the plain recursive NN achieves only
  mixed results in all three experiments, whereas the stronger RNTN
  model generalizes well in every case, suggesting that it has in fact
  learned, or at least learned to simulate, our target logical
  concepts.}

>>>>

In our first set of experiments, we use this pre-specified logical
grammar to generate controlled data sets encoding the semantic
relationships between pairs of expressions and evaluate whether each
of two classes of neural model---plain recursive NNs and recursive neural
tensor networks (RNTNs; \citealt{socher2013acl1})---can learn those
relationships correctly. In our first experiment
(Section~\ref{sec:join}), we evaluate the ability of these models to
learn the core relational algebra of natural logic from data. Our
second experiment (Section~\ref{sec:recursion}) extends this
evaluation to relations between complex recursive structures like
$(a \plor b)$ and $\plneg (\plneg a \pland \plneg b)$, and our third
experiment (Section~\ref{sec:quantifiers}) involves relations between
quantified statements like \ii{every reptile walks} and \ii{no turtle
  moves}. \tbchecked{We find that the plain recursive NN achieves only
  mixed results in all three experiments, whereas the stronger RNTN
  model generalizes well in every case, suggesting that it has in fact
  learned, or at least learned to simulate, our target logical
  concepts.}

### 2014-12-02 writing/F'14 paper/join.tex
Paper TODO tweaks

    \bottomrule
  \end{tabular}
  \caption{Performance on the semantic relation experiments. These results and all other results on artificial data are reported as mean accuracy scores over five runs followed by mean macroaveraged F1 scores in parentheses.}
  \label{joinresultstable}
\end{table}

@@

\paragraph{Results} 
Table \ref{joinresultstable} shows the results, which are fairly straightforward 
to interpret. Both models were able to accurately encode the relations 
between the terms in the geometric relations between their vectors, 
and was able to then use that information to recover relations that 
were not overtly included in the training data.  The model's slightly 
poorer performance on the unprovable test examples shows that it
 has not simply encoded an approximation the entire underlying 
 model, but is rather taking advantage of the specific statements seen in the test data.

>>>>

    \bottomrule
  \end{tabular}
  \caption{\mynote{Performance on the semantic relation experiments.} These results and all other results on artificial data are reported as mean accuracy scores over five runs followed by mean macroaveraged F1 scores in parentheses.}
  \label{joinresultstable}
\end{table}

@@

\paragraph{Results} 
Table \ref{joinresultstable} shows the results, which are fairly straightforward 
to interpret. Both models were able to accurately encode the relations 
between the terms in the geometric relations between their vectors, 
and was able to then use that information to recover relations that 
were not overtly included in the training data.  \tbchecked{The model's slightly 
poorer performance on the unprovable test examples shows that it
 has not simply encoded an approximation the entire underlying 
 model, but is rather taking advantage of the specific statements seen in the test data.}
